\vskip-0.6in \Large Political Uncertainty

### 2016-02-09 two-groups.tex
revisse vote buyer B portion of sec: solve

\item Vote buyer B
		\begin{itemize}
			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''
			\item This has to be adapted to our situation with uncertainty
				\begin{itemize}
					\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
					\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
					\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
					\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
					\item Some legislators who are past FOC point will not be lobbied
				\end{itemize}
		\end{itemize}

			\item Need to max probability of at least two voting ``no'': $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$
			\item Thus, maximization problem for Vote Buyer B (in absence of Vote Buyer A) is
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}
			Substituting from the definition of $X$,
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \left(1-\frac{1}{1+e^{-Y}}\right)  + \\
					\frac{1}{1+e^{-Z}} \left(1-\frac{1}{1+e^{-X}}\right) \frac{1}{1+e^{-Y}} + \\
					\left(1-\frac{1}{1+e^{-Z}} \right) \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} + \\
					\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}
			This can be simplified as 
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} +
					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-Z}} + \\
					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
					\label{eq:obj}
				\end{multline}

			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is 
				\begin{equation}
					W_B \biggl[ \left( \frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2 \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \right) \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
				\end{equation}
			Simplifying:
			\begin{equation}
					W_B \biggl[ \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
					\label{eq:logistic}
				\end{equation}
			Further math related to this equation is on Page~\pageref{eq:logistic2}.

	\item Some notes
		\begin{itemize}
			\item If we divide through by 2, the left side is the average minus the product
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
		\end{itemize}

\end{enumerate}

\section{Adding Vote Buyer A}

@@

\newpage
\subsection{Math for Discrete Model}
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		and
		\begin{equation}
			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
			\label{eq:base}
		\end{equation}
		Setting the left-hand size of these last two equations (the FOCs for the bribes for 0 and $\frac{1}{2}$ equal to each other,
		\[
		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
		\]
		\[
		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
		\]
		\[
		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
		\]
		\begin{equation}
		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
			\label{eq:twoways}
		\end{equation}
   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
		\[
		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
		\]
		\begin{equation}
		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
			\label{eq:1}
		\end{equation}
  	Second, multiplying through by zero:
	  \begin{equation}
		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
			\label{eq:2}
		\end{equation}
	\end{itemize}	
In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(-\frac{1}{2}\right)$, we know that $Z < 0$. Note that this is due to the construction of the problem. This means $e^Z < 1$. In this case,
	\begin{itemize}
		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
	\end{itemize}
The second order conditions will pin down the solution in this case of two non-negative bribes.

>>>>

\item Vote buyer B
		\begin{itemize}
			\item GS assumption on vote buyers' objective is ``each prefers to minimize total bribes paid while passing his preferred policy, but each would prefer to concede the issue rather than pay more than his WTP''; this has to be adapted to our situation with uncertainty
			\item With asymmetric $v(z)$ or WTP parameters, it would be easy to get equilibria where only $A$ or $B$ buys votes. But we also have lots of outcomes where both buy votes.
			\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
			\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
			\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
			\item Some legislators who are past FOC point will not be lobbied		
			\item Need to max probability of at least two voting ``no'': $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$
			\item Thus, maximization problem for Vote Buyer B (in absence of Vote Buyer A) is
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(\frac{1}{2}\right)=0\right)  + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) + \\
					\Pr\left(X\left(-\frac{1}{2}\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(\frac{1}{2}\right)=1\right) \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}
			Substituting from the definition of $X$,
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \left(1-\frac{1}{1+e^{-Y}}\right)  + \\
					\frac{1}{1+e^{-Z}} \left(1-\frac{1}{1+e^{-X}}\right) \frac{1}{1+e^{-Y}} + \\
					\left(1-\frac{1}{1+e^{-Z}} \right) \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} + \\
					\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
				\end{multline}
			This can be simplified as 
			  \begin{multline}
			    \max_{b\left(-\frac{1}{2}\right), b\left(0\right), b\left(\frac{1}{2}\right)} 
					W_B \biggl[ \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} +
					\frac{1}{1+e^{-X}} \frac{1}{1+e^{-Z}} + \\
					\frac{1}{1+e^{-Y}} \frac{1}{1+e^{-Z}} - 2	\frac{1}{1+e^{-Z}} \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} b(j)
					\label{eq:obj}
				\end{multline}

			The FOC wrt to $b\left(-\frac{1}{2}\right)$ is 
				\begin{equation}
					W_B \biggl[ \left( \frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2 \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \right) \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
				\end{equation}
			Simplifying:
				\begin{equation}
					W_B \biggl[ \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
					\label{eq:logistic}
				\end{equation}
			Further math related to this equation is on Page~\pageref{eq:logistic2}.
			\item If we divide through by 2, the left side is the average minus the product
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
		\end{itemize}
	\item Vote Buyer A
\end{enumerate}

@@

\newpage
\section{Math for Discrete Model}
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		and
		\begin{equation}
			\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
			\label{eq:base}
		\end{equation}
		Setting the left-hand size of these last two equations (the FOCs for the bribes for 0 and $\frac{1}{2}$ equal to each other,
		\[
		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
		\]
		\[
		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
		\]
		\[
		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
		\]
		\begin{equation}
		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
			\label{eq:twoways}
		\end{equation}
   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
		\[
		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
		\]
		\begin{equation}
		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
			\label{eq:1}
		\end{equation}
  	Second, multiplying through by zero:
	  \begin{equation}
		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
			\label{eq:2}
		\end{equation}
	\end{itemize}	
In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(-\frac{1}{2}\right)$, we know that $Z < 0$. Note that this is due to the construction of the problem. This means $e^Z < 1$. In this case,
	\begin{itemize}
		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
	\end{itemize}
The second order conditions will pin down the solution in this case of two non-negative bribes.
